\section{Development}
    \subsection{REST API}
        \begin{frame}[t]{Developing the REST API}\framesubtitle{Overview}
            \begin{itemize}
                \item Focus on the next generation of GIRAF developers
                \begin{itemize}
                    \item Documentation
                    \item Design
                \end{itemize}
                \item Synchronisation
                \item Security
            \end{itemize}
        \end{frame}

        \begin{frame}[t]{Developing the REST API}\framesubtitle{Our contributions}
            Sprints 3-4:
            \begin{itemize}
                \item Pictograms
                \item Sequences
                \item Week Schedules
            \end{itemize}
            \bigskip
            Differences from developing Apps.
            \begin{itemize}
                \item Unit Tests (With a code--coverage above 0~\%)
                \item Linting
                \begin{itemize}
                    \item Saved time during code--review
                    \item Enforced a code--style
                \end{itemize}
                \item Strict(er) code--review
            \end{itemize}
        \end{frame}

        \begin{frame}[t]{Demo of the REST API}\framesubtitle{Pictograms and Sequences}
            The demo will show:
            \begin{itemize}
                \item Pictograms
                \begin{itemize}
                    \item being uploaded.
                    \item being viewed.
                \end{itemize}
                \item Sequences
                \begin{itemize}
                    \item being created.
                    \item being viewed.
                    \item being edited.
                \end{itemize}
            \end{itemize}
        \end{frame}

    \subsection{GIRAF--Apps}
        \begin{frame}[t]{GIRAF--Apps}
            Sprints 1-2:
            \begin{itemize}
                \item Gradle issues
                \item PictoSearch library
                \item Week Schedule
            \end{itemize}
        \end{frame}


        \subsubsection{Gradle}
            \begin{frame}[t]{GIRAF--Apps}\framesubtitle{The Gradle Build System}
                \begin{itemize}
                    \item Fixing the initial broken library builds.
                    \item Assisting with Jenkins.
                    \item Helping various groups with small issues.
                \end{itemize}
            \end{frame}

        \subsubsection{PictoSearch}
            \begin{frame}[t]{GIRAF--Apps}\framesubtitle{PictoSearch}
                \begin{itemize}
                    \item Improving the initial view.
                    \item \enquote{real--time} search.
                \end{itemize}
                \bigskip
                \begin{columns}[c]
                    \column{0.5\textwidth}
                        Before screenshot
                    \column{0.5\textwidth}
                        After screenshot (Animation?)
                \end{columns}
            \end{frame}

        \subsubsection{Week Schedule}
            \begin{frame}[t]{GIRAF--Apps}\framesubtitle{Week Schedule}
                \begin{itemize}
                    \item Added border to each frame.
                    \item Made the entire area scrollable.
                \end{itemize}
                \bigskip
                \begin{columns}[c]
                    \column{0.5\textwidth}
                        Before screenshot
                    \column{0.5\textwidth}
                        After screenshot (Animation?)
                \end{columns}
            \end{frame}
